%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Software Engineer · Angular(TypeScript), .NET(C\#)} % Job title
  {Dodge Construction Network} % Organization
  {Vancouver, Canada} % Location
  {Feb. 2020 - Jan. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Spearheaded front-end architecture of construction data platform to support 12+ developers over 3 teams in writing efficient code, reducing overall code review time.}
      \item {Refined and planned sprints as part of a scrum team by maintaining consistency between upcoming features and existing requirements.}
      \item {Implemented major parts of an automated email scrapping system, utilizing asynchronous processes such as schedulers and lambdas to aggregate and store data.}
      \item {Overhauled our HTML to PDF service by replacing previous rendering library with in-house solution, improving export times and reducing compute resource cost.}
      \item {Designed developed, and documented APIs utilizing .NET framework to communicate with various back-end services and facilitate features on the front-end.}
      \item {Enhanced overall security of our web applications by implementing content security policy and investigating avenues for injection attacks.}
      \item {Rebuilt legacy ASP.NET MVC product with Angular front-end to reduce server load and decrease client-application load times.}
      \item {Isolated business logic from MVC-controllers and exposed them under new RESTful APIs to better support client-sided web development.}
      \item {Upgraded CI/CD development process with Git hooks and SonarQube to maintain passing unit tests, consistent branch names and commit messages, and perform code quality analysis automatically.}
      \item {Mentored juniors and contractor teams to identify code smells and design pitfalls in order to maintain best practices and reduce technical debt.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Junior Quality Engineer · Protractor(TypeScript), Karate(Java)} % Job title
  {} % Organization
  {} % Location
  {Nov. 2018 - Dec. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Automated end-to-end and API test cases with Protractor in TypeScript and Karate in Java to drastically speed up regression analysis.}
      \item {Refactored larger portions of automation code base written by multiple team members to reduce code duplication and increase maintainability.}
      \item {Performed root cause analysis on defects by tracing application dataflow, enabling more detailed logging and reducing the debugging effort on developers.}
      \item {Designed efficient test cases based on user stories and requirements to create a streamlined and effective acceptance testing environment.}
      \item {Managed, mentored, and performed test case and automation code reviews for our QA team to lead our software test lifecycle.}
      \item {Participated in progress meetings to ensure well integrated processes between development and QA teams.}
    \end{cvitems}
  }


%---------------------------------------------------------
\end{cventries}
